A radiocarbon data based evaluation of Cultural Transmission in Bronze Age burial rites of Central, Northern and North-western Europe

### 2018-12-17 article/03_Results.Rmd
improvements of "Northern Germany"

`r a("Northern Germany")`:
The artificial region *Northern Germany* includes all new federal states in East Germany, but also large parts of Lower Saxony and Schleswig-Holstein. The ^14^C data for this region come mainly from Saxony-Anhalt and neighbouring regions in Thuringia, Saxony and Lower Saxony. Also from the area north of Bremen some data are documented in Radon-B. The database does not contain as many dated graves from any other region as from northern Germany. Most of them date back to the Early Bronze Age, while the Middle Bronze Age from about 1800calBC to 1400calBC is a striking period for some centuries. Only for the Late Bronze Age is a significant number of data documented again. The meta information on *burial type* and *burial construction* trace this development to about the same extent.  Since in Northern Germany influences from all four cardinal points come together and contribute significantly to the formation of local cultural phenomena, it is difficult to estimate the overall development of the primary variables here as well. The ^14^C proxy correctly represents *burial site* insofar as bodily burials dominated in the Early Bronze Age and are replaced by burials especially in the North from the Middle Bronze Age onwards. In the Late Bronze Age cremation was clearly more dominant than the data set suggests. With regard to *burial construction*, the current Radon-B stock records the basic dominance of flat graves well, but attributes more relevance to them in the Early and Middle Bronze Age than is usual in the archaeological assessment of the context.

>>>>

`r a("Northern Germany")`:
The artificial region *Northern Germany* includes all federal states in East Germany, but also large parts of Lower Saxony and Schleswig-Holstein. The ^14^C data for this region come mainly from Saxony-Anhalt and neighbouring regions in Thuringia, Saxony and Lower Saxony. Also from the area north of Bremen some data are documented in Radon-B. The database does not contain as many dated graves from any other region as from northern Germany. Most of them date back to the Early Bronze Age, while the Middle Bronze Age from about 1800calBC to 1400calBC seems barren. Only for the Late Bronze Age there is a significant number of data documented again. The meta information on *burial type* and *burial construction* trace this development to the same extent. Since in Northern Germany influences from all four cardinal points come together and contribute significantly to the formation of local cultural phenomena, it is difficult to estimate the overall development of the primary variables here as well. The ^14^C proxy correctly represents *burial site* insofar as inhumations dominated in the Early Bronze Age and are replaced by cremations especially in the North from the Middle Bronze Age onwards. In the Late Bronze Age though, cremation was clearly more dominant than the data set suggests. With regard to *burial construction*, the current Radon-B stock records the basic dominance of flat graves well, but attributes more relevance to them in the Early and Middle Bronze Age than is usual in the archaeological assessment of the context.
